Cell Decompositions for Rank Two Quiver Grassmannians

### 2019-06-28 Grassmannian_cells.tex
Clean up

\begin{theorem}
  \label{celldec}
  The following hold:
  \begin{enumerate}
    \item Every quiver Grassmannian of any indecomposable preprojective or preinjective representation of $K(n)$ and $\widetilde{K(n)}$ has a cell decomposition.
    \item Let $X\in\rep K(n)$ be an indecomposable representation with dimension vector $(d,e)$ or $(e,d)$, where $(d,e)=\udim P_{m+1}-r\udim P_m$ for $m\geq 1$ and $\leq 0\leq r\leq n-1$.
      Then every quiver Grassmannian $\Gr_\bfe(X)$ has a cell decomposition.
  \end{enumerate}
\end{theorem}
\begin{proof}Both claims follow by considering iterated torus actions taking into account that all quiver Grassmannians under consideration are smooth. For the truncated preprojective representations of $K(n)$ this is Theorem~\ref{thm:truncpp}. For the truncated preprojective representations lifted to the iterated universal abelian covering quivers $\widehat{K(n)}^{(k)}$ for $k\geq 1$, it follows inductively - when applying reflection recursions similar to those stated in (\ref{eq:recursive covers}) -  that these lifts are exceptional representations of $\widehat{K(n)}^{(k)}$, which means that their quiver Grassmannians are again smooth. Note that this is indeed clear for $m= 2$.

@@

While the cell decompositions above appear to depend on the data built into their recursive construction, the compatibility condition ($\dagger$) implies these cell decompositions exhibit a remarkable amount of recursive symmetry.
\begin{corollary}
  Fix an admissible sequence $\ui=(i_1,\ldots,i_k)$, $k<m$, and subsets $I,J\subsetneq\{1,\ldots,n\}$ with $i_1\notin J$ and $i_k\in I$.
  Let $\tilde K_m=\tilde K_m(\ui,I,J)$ denote the kernel of the projection $\tilde\pi_{m+1}^{\ui,I,J}:\tilde P_{m+1}^J\to \tilde P_{m+1-k,\ui}^I$.
  For any dimension vectors $\tbfe,\tbff,\tbfg$ with $\tbfe=\tbff+\tbfg$, and any affine cell $A_\tbfe$ of $Gr_\tbfe(\tilde P_{m+1}^J)$ which intersects the preimage under the Caldero-Chapoton map of a product of affine cells $B_\tbff\times C_\tbfg$ from $Gr_\tbff(\tilde K_m)\times Gr_\tbfg(\tilde P_{m+1-k,\ui}^I)$, we have $\Psi(\tilde E)\in B_\tbff\times C_\tbfg$ for all $\tilde E\in A_\tbfe$.
  Moreover, the induced map $A_\tbfe\to B_\tbff\times C_\tbfg$ is surjective with affine fibers.
\end{corollary}
\begin{proof}
  \begin{itemize}
    \item Implicit in the construction of the cell decomposition for $\Gr_\tbfe(\tilde P_{m+1}^J)$ is a choice of complete filtration for $\tilde P_{m+1}^J$ by subrepresentations of the form $\tilde K_m(\ui',I',J)$.
      In Section~\ref{sec:2quivers}, we fix a standard convention.

    \item By the compatibility of the cell $A_\tbfe$ with the map $\tilde\pi_{m+1}^{\ui,I,J}$, we have $\tilde\pi_{m+1}^{\ui,I,J}(\tilde E)\ne 0$ for all $\tilde E\in A_\tbfe$.
  \end{itemize}

  Suppose the cell $A_\tbfe$ was constructed inductively using $J\subsetneq I'\subsetneq \{1,\ldots,n\}$ with $I'\setminus J=\{j\}$.
\end{proof}

>>>>

\begin{theorem}
  \label{celldec}
  The following hold:
  \begin{enumerate}
    \item Every quiver Grassmannian of any indecomposable preprojective or preinjective representation of $K(n)$ and $\widetilde{K(n)}$ has a cell decomposition.
    \item Let $X\in\rep K(n)$ be an indecomposable representation with dimension vector $(d,e)$ or $(e,d)$, where $(d,e)=\udim P_{m+1}-r\udim P_m$ for $m\geq 1$ and $\leq 0\leq r\leq n-1$.
      Then every quiver Grassmannian $\Gr_\bfe(X)$ has a cell decomposition.
  \end{enumerate}
\end{theorem}
\begin{proof}
  Both claims follow by considering iterated torus actions taking into account that all quiver Grassmannians under consideration are smooth.
  For the truncated preprojective representations of $K(n)$, this is Theorem~\ref{thm:truncpp}.
  For the truncated preprojective representations lifted to the iterated universal abelian covering quivers $\widehat{K(n)}^{(k)}$ for $k\geq 1$, it follows inductively -- when applying reflection recursions similar to those stated in (\ref{eq:recursive covers}) --  that these lifts are exceptional representations of $\widehat{K(n)}^{(k)}$, which means that their quiver Grassmannians are again smooth.
  Note that this is indeed clear for $m= 2$.

@@
